Vaccines: Many Beliefs Study 3: Overparenting deep dive

### 2018-10-22 study1/custom-structure-learning-vaccData.Rmd
updates ahead of talk

# source("cog-model-graph-tools.R")
source("../scripts/custom-structure-learning/cog-model-main.R")
source("../scripts/gmod_tools.R")
source("../scripts/bnTheoryBlacklist.R")

@@

compute_scoretables <- FALSE # uncomment to recompute scoretables
source("fit-cog-models.R")

@@

all_results <- readRDS("allresults.rds")
```

@@

BiDAG_traceplot(all_results[[1]], hide = 1, show_chains=c(1,2,3,4))
# BiDAG_traceplot(all_results[[3]], hide = 100, show_chains=c(3,4))
```

@@

```{r}
merged_chains <- merge_chains(all_results[[1]][2:4])
map_dag <- extract_mapdag(merged_chains)

@@

plt.valid <- test_analyze %>%
  ggplot(aes(x=predValue, y=value)) + 
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha=.33) +
  geom_point(shape=1, size=.5, color="darkturquoise") + 
  geom_text(data=corrDF, aes(label=paste("r =", cor)),
            x=-Inf, y=Inf, hjust=-0.12, vjust=1.4,
            size = 10*.352777778,
            color="grey25") +
  # geom_smooth(method="lm") +
  theme_bw(base_size = 10) +
  theme(strip.background = element_rect(fill="grey90"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  coord_fixed() + 
  facet_wrap(~varName, nrow=2) + 
  scale_x_continuous("Predicted values", limits = c(0, 1)) +
  scale_y_continuous("Observed values", limits = c(0, 1))

>>>>

# source("cog-model-graph-tools.R")
source("../scripts/custom-structure-learning/cog-model-main.R", chdir = TRUE)
source("../scripts/gmod_tools.R")
source("../scripts/bnTheoryBlacklist.R")

@@

compute_scoretables <- FALSE # uncomment to recompute scoretables
source("../scripts/custom-structure-learning/fit-cog-models.R", chdir=TRUE)

@@

all_results <- readRDS("../local/allresults.rds")
```

@@

BiDAG_traceplot(all_results[[5]], hide = 1, show_chains=c(1,2,3,4))
# BiDAG_traceplot(all_results[[3]], hide = 100, show_chains=c(3,4))
```

@@

```{r}
merged_chains <- merge_chains(all_results[[5]][1:4])
map_dag <- extract_mapdag(merged_chains)

@@

plt.valid <- test_analyze %>%
  ggplot(aes(x=predValue, y=value)) + 
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha=.33) +
  geom_point(shape=1, size=.5, color="darkturquoise") + 
  geom_text(data=corrDF, aes(label=paste("r =", cor)),
            x=-Inf, y=Inf, hjust=-0.12, vjust=1.4,
            size = 10*.352777778,
            color="grey25") +
  # geom_smooth(method="lm") +
  coord_fixed() + 
  facet_wrap(~varName, nrow=2) + 
  scale_x_continuous("Predicted values", limits = c(0, 1)) +
  scale_y_continuous("Observed values", limits = c(0, 1)) +
  theme_bw(base_size = 10) +
  theme(strip.background = element_rect(fill="grey90"), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

### 2018-10-22 study2/vacc_manyBelief_study2_overpar.Rmd
refactored, working
updates ahead of talk

```{r tidy, include = F}
# load data
d_all <- read.csv("data/study3_data.csv")[-1]

@@

>>>>

```{r tidy, include = F}
# load data
d_all <- read.csv("../data/study2_data.csv")[-1]

@@

# Bayesian regularized regression

This is interesting and a great setup, but I'm having a bit of trouble interpreting 3-4 way interactions ...

```{r}
library(brms)

rescale_beta <- function(x, lower, upper) {
  # rescales onto the open interval (0,1)
  # rescales over theoretical bounds of measurement, specified by "upper" and "lower"

  N <- length(x)
  res <- (x - lower) / (upper - lower)
  res <- (res * (N - 1) + .5) / N

  return(as.vector(res))
}

fit <- brm(
  vaccIntent ~ phase * condition * overpar * medSkept * diseaseSevere + (1|workerId),
  prior = set_prior("normal(0,.5)", class = "b"),
  family = Beta(),
  data = d_scored_wide %>% 
    mutate(vaccIntent = rescale_beta(vaccIntent, 
                                     min(d_scored_wide$vaccIntent), 
                                     max(d_scored_wide$vaccIntent)
                                     )),
  control = list(adapt_delta = .90, max_treedepth = 15),
  chains = 2,
  cores = 2
)
```

```{r}
summary(fit)
```

I don't think any of these interaction terms are coming out "significant." Certainly all the phasepost:conditionDR involved ones are not. Closest looks like phasepost:conditionDR:overpar:medskept.

```{r}
fit_pre <- brm(
  vaccIntent ~ overpar * medSkept * diseaseSevere + (1|workerId),
  prior = set_prior("normal(0,.5)", class = "b"),
  family = Beta(),
  data = d_bn %>% 
    mutate(vaccIntent = rescale_beta(vaccIntent, -3, 3), workerId = 1:nrow(d_bn)),
  control = list(adapt_delta = .90, max_treedepth = 15),
  chains = 2,
  cores = 2
)
```

```{r}
summary(fit_pre)
```
